working title Compatibility system and stygma size of pollen recipient as main predictors of heterospecific pollen effect

### 2018-12-11 Manuscript_draft/Manuscript_draft.Rmd
Table transferred to Markdown

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE,fig.height=4,fig.width=5, fig.cap="The effect of heterospecific pollen (scaled see set) is represented in function of the compatibility system (self/cross*100) for the the different species. Each coulored dot represents the interaction of a focal species with a different pollen donor."}
load("myEnv.RData")
library(nlme)
library(lme4)
library(ggplot2)
library(cowplot)
model2=lme(hp_effect~compatibility, data=ALL, random=~1|indv)
ggplot(ALL, aes(x=compatibility, y=hp_effect)) + 
  geom_jitter(width=1.5,aes(colour = Focal),size=4)+
  geom_abline(aes(intercept=`(Intercept)`, slope=compatibility), as.data.frame(t(fixef(model2))))+theme_cowplot()

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE}
library(kableExtra)
load("table_treatments.RData")

table<- data.frame(cross, self, nat_self,apo)
kable(table, format="markdown")
```

@@

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE,fig.height=4,fig.width=5, fig.cap="The effect of heterospecific pollen (scaled see set) is represented in function of the compatibility system (self/cross*100) for the the different species. Each coulored dot represents the interaction of a focal species with a different pollen donor."}
load("myEnv.RData")
library(nlme)
library(lme4)
library(ggplot2)
library(cowplot)
model2=lme(hp_effect~compatibility, data=ALL, random=~1|indv)
ggplot(ALL, aes(x=compatibility, y=hp_effect)) + 
  geom_jitter(width=1.5,aes(colour = Focal),size=4)+
  geom_abline(aes(intercept=`(Intercept)`, slope=compatibility), as.data.frame(t(fixef(model2))))+theme_cowplot()
